Storm surge modelling in the Strait of Georgia

### 2014-10-14 RoughWork/manuscript.tex
Modified tables to include mean of obs/mod

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c | c c c|} 
\hline 
& \multicolumn{3}{|c|}{Water Level ($\eta$)}        & \multicolumn{3}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\gamma^2$ & $WS$      \\
\hline 
Point Atkinson & 10.5           &   0.012    & 0.994  & 6.2            &  0.065     & 0.979     \\
Victoria       &  8.6           &   0.032    & 0.992  & 6.1            &  0.085     & 0.970     \\
Patricia Bay   &  9.1           &   0.024    & 0.992  & 6.9            &  0.070     & 0.969     \\
Campbell River & 13.1           &   0.041    & 0.990  & 5.8            &  0.079     & 0.961     \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Feb 2006 simulation. Mean absoulte error ($\bar{e}$), $\gamma^2$, and the Willmott skill score ($WS$) are provided for water level predictions ($\eta$) and resdiuals ($\delta$) during the period displayed in Figure \ref{fig:feb2006}.}
\label{tab:feb2006stat} 
\end{table} 
%anything else to include? statistics calculated in Feb 2006 -paper prodcution.ipynb and saved in statisitcs_feb2006.csv 
%mean of model and mean of observations?

@@

Point Atkinson observed a maximum surge amplitude of 84 cm, which is approximately 28 cm higher than the modelled residual, however the timing of the surge agrees almost exactly as displayed in Figure \ref{fig:dec2006}. The best agreement occurs at Victoria where the observed surge was 62 cm and the model returned 44 cm. At all of the locations, the model predicted the maximum surge to occur within 3.5 hours of the observed surge. Typically, the modelled surge was too early, in contrast to the later predictions in the Feb 4, 2006 case. Error and skill scores for the modelled water level and the modelled residual are provided in Table \ref{dec2006stat}. The modelled residuals are on average too low and have a lower skill score than the Feb 2006 case. This could be due to a number of factors. First,the very large wind speeds observed during this storm are significantly underrepresented by the atmospheric model leading to lower wind stress and less piling of water against the coast. Second, the anomaly forcing at the open boundaries could be too low. The observed residual at Tofino, BC (a point near by but outside of the domain) is up to 10 cm lower than the observed residual at Neah Bay, WA (a point near by but inside of the domain). Since the storm surge is less sensitive to wind forcing at the surface than anomaly forcing at the open boundaries, the latter is likely the case. 
%Skill score between CGRF and observed winds?

@@

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{m}}$ (o) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Point Atkinson & 10.5           &  3.45                & 3.47                 &   0.025    & 0.994  & 11.1           &  0.212                 & 0.186                  &  0.275     & 0.891 \\
Victoria       &  9.6           &  2.23                & 2.16                 &   0.042    & 0.984  &  7.9           &  0.190                 & 0.156                  &  0.223     & 0.911 \\
Patricia Bay   &  9.2           &  2.63                & 2.58                 &   0.031    & 0.990  &  9.5           &  0.193                 & 0.149                  &  0.260     & 0.889 \\
Campbell River & 10.6           &  3.23                & 3.28                 &   0.030    & 0.992  & 10.6           &  0.191                 & 0.163                  &  0.247     & 0.905 \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Dec 2006 simulation.}
\label{tab:dec2006stat} 
\end{table}

@@

Once again, an evaluation of the model skill in this hindcast is provided in Table \ref{tab:nov2009stats}.

>>>>

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Point Atkinson & 10.5           & 3.46                 & 3.54                 &   0.012    & 0.994  & 6.2            &  0.273                 & 0.309                  & 0.065     & 0.979     \\
Victoria       &  8.6           & 2.18                 & 2.19                 &   0.032    & 0.992  & 6.1            &  0.235                 & 0.278                  & 0.085     & 0.970     \\
Patricia Bay   &  9.1           & 2.60                 & 2.64                 &   0.024    & 0.992  & 6.9            &  0.223                 & 0.278                  & 0.070     & 0.969     \\
Campbell River & 13.1           & 3.20                 & 3.21                 &   0.041    & 0.990  & 5.8            &  0.303                 & 0.300                  & 0.079     & 0.961     \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Feb 2006 simulation. Mean absoulte error ($\bar{e}$), $\gamma^2$, and the Willmott skill score ($WS$) are provided for water level predictions ($\eta$) and resdiuals ($\delta$) during the period displayed in Figure \ref{fig:feb2006}.}
\label{tab:feb2006stat} 
\end{table} 
%anything else to include? statistics calculated in Feb 2006 -paper prodcution.ipynb and saved in statisitcs_feb2006.csv 
%mean of model and mean of observations?

@@

Point Atkinson observed a maximum surge amplitude of 84 cm, which is approximately 28 cm higher than the modelled residual, however the timing of the surge agrees almost exactly as displayed in Figure \ref{fig:dec2006}. The best agreement occurs at Victoria where the observed surge was 62 cm and the model returned 44 cm. At all of the locations, the model predicted the maximum surge to occur within 3.5 hours of the observed surge. Typically, the modelled surge was too early, in contrast to the later predictions in the Feb 4, 2006 case. Error and skill scores for the modelled water level and the modelled residual are provided in Table \ref{tab:dec2006stat}. The modelled residuals are on average too low and have a lower skill score than the Feb 2006 case. This could be due to a number of factors. First,the very large wind speeds observed during this storm are significantly underrepresented by the atmospheric model leading to lower wind stress and less piling of water against the coast. Second, the anomaly forcing at the open boundaries could be too low. The observed residual at Tofino, BC (a point near by but outside of the domain) is up to 10 cm lower than the observed residual at Neah Bay, WA (a point near by but inside of the domain). Since the storm surge is less sensitive to wind forcing at the surface than anomaly forcing at the open boundaries, the latter is likely the case. 
%Skill score between CGRF and observed winds?

@@

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Point Atkinson & 10.5           &  3.45                & 3.47                 &   0.025    & 0.994  & 11.1           &  0.212                 & 0.186                  &  0.275     & 0.891 \\
Victoria       &  9.6           &  2.23                & 2.16                 &   0.042    & 0.984  &  7.9           &  0.190                 & 0.156                  &  0.223     & 0.911 \\
Patricia Bay   &  9.2           &  2.63                & 2.58                 &   0.031    & 0.990  &  9.5           &  0.193                 & 0.149                  &  0.260     & 0.889 \\
Campbell River & 10.6           &  3.23                & 3.28                 &   0.030    & 0.992  & 10.6           &  0.191                 & 0.163                  &  0.247     & 0.905 \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Dec 2006 hindcast.}
\label{tab:dec2006stat} 
\end{table}

@@

Once again, an evaluation of the model skill for this hindcast is provided in Table \ref{tab:nov2009stat}.

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Point Atkinson & 14.0           &  3.45                & 3.55                 &   0.012    & 0.995  &  6.1           &  0.313                 & 0.331                  &  0.237     & 0.913 \\
Victoria       &  9.9           &  2.25                & 2.24                 &   0.023    & 0.989  &  4.8           &  0.323                 & 0.293                  &  0.245     & 0.899 \\
Patricia Bay   & 11.2           &  2.50                & 2.65                 &   0.020    & 0.997  &  6.0           &  0.277                 & 0.290                  &  0.272     & 0.901 \\
Campbell River & 13.5           &  3.22                & 3.27                 &   0.019    & 0.991  &  4.9           &  0.326                 & 0.314                  &  0.217     & 0.924 \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Nov 2009 hindcast.}
\label{tab:nov2009stat} 
\end{table}
